The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-19 document/ms.tex
comments from hogg

\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\uw},
    Timothy~D.~Morton\altaffilmark{\princeton},
    David~W.~Hogg\altaffilmark{\scda,\nyu,\mpia,\cds},
    Eric~Agol\altaffilmark{\uw},
    Bernhard~Sch\"olkopf\altaffilmark{\mpis},
    and others
}

@@

The \kepler\ Mission has discovered thousands of exoplanets and revolutionized
our understanding of their population.
This large, homogeneous catalog of discoveries has enabled rigorous studies of
the occurrence rate of exoplanets and planetary systems as a function of their
physical properties.
Transit surveys like \kepler\ are most sensitive to planets with shorter
orbital periods than the gas giant planets that dominate the dynamics of our
Solar System.
We performed a fully automated search for long-period exoplanets with only one
or two transits in the archival \kepler\ light curves.
When applied to the 40,000 brightest Sun-like target stars, this search
produces \numcands\ long-period exoplanet candidates.
Since our method involves no human intervention, we empirically characterize
the completeness and reliability of our search.
Based on these results, we measure the average occurrence rate of exoplanets
smaller than Jupiter with orbital periods longer than two years.

@@

Data from the \kepler\ Mission \citep{Borucki:2011} has been used to discover
thousands of transiting exoplanets.
The systematic nature of these discoveries and careful quantification of
survey selection effects, search completeness, and catalog reliability has
enabled many diverse studies of the detailed frequency and distribution of
exoplanets \citep[for example,][]{Howard:2012, Petigura:2013,
Foreman-Mackey:2014, Dressing:2015, Burke:2015, Mulders:2015}.
So far, these results have been limited to relatively short orbital periods
because existing transit search methods require the observation of at least
three transits within the baseline of the data.
For \kepler, with a baseline of about four years, this sets an absolute upper
limit on the detectable periods of about two years.
In the Solar System, Jupiter~--~with a period of 12 years~--~dominates the
planetary dynamics and, since it would only exhibit at most one transit in the
\kepler\ data, an exo-Jupiter would be missed by most existing transit search
procedures.

@@

The occurrence rates given here should be interpreted with a few caveats in
mind.
First, when we inferred the periods of the planets with only one transit, we
assumed that the period was long enough that no other transit occurred during
the \kepler\ lifetime.
This neglects the small but non-negligible probability~--~less than one
percent for the typical candidate~--~that a second transit might have
occurred in a data gap.
All of the candidates in our catalog are consistent with having periods this
long but the geometric transit probability decreases quickly with orbital
period.
For the purposes of this \paper, we neglect this effect because its rigorous
treatment is subtle.

@@

\citet{Clanton:2014} studied the occurrence rate of long-period giant planets
orbiting M-dwarfs by combining results from radial velocity and microlensing
surveys.
In the period and mass range $10^3-10^4\unit{days}$ and $10-10^4\,M_\oplus$,
they find a mean occurrence rate density of
\begin{eqnarray}
\frac{\dd^2 N}{\dd\ln M/M_\mathrm{J}\,\dd\ln P/\unit{yr}}
    &\lesssim& 0.026
\end{eqnarray}
per M-dwarf.
This result is slightly lower than our estimated rate for a similar range of
masses and periods but around G/K dwarfs.
This difference is consistent with previous results that cooler stars host
fewer long-period giant planets \citep[for example][]{Cumming:2008}.

@@

\tablenotetext{a}{The rate density is measured in natural logarithmic units.}
\tablecomments{These values are computed assuming that the occurrence rate is
flat in the logarithmic parameters.}
\end{deluxetable}
\end{floattable}

@@

The single-visit precision of \gaia\ will vary with magnitude but is expected
to be on the order of 40\,$\mu$as at these magnitudes.
In detail the confidence with which an exoplanet can be detected or measured
in the final \gaia\ data depends on this precision, the number of crossings of
the star through the \gaia\ focal plane, and details of how the projected
orbit is sampled by the time history of the focal-plane crossings.
However, it is not expected that \gaia\ can detect or measure precisely
exoplanet-induced astrometric wobbles that are much smaller in amplitude than
the single-visit precision \citep{Perryman:2014}.

The primary stars in the \kepler\  Field are typically at distances of $\sim
500$\,pc, and typical mass ratios are in the $10^{-4}$ range.
We therefore expect astrometric amplitudes in the 0.3 to 3\,$\mu$as range.
These planets will not be detectable or measurable in the \gaia\ data under
any circumstances.
However, similar planets around closer stars \emph{will} be detectable with
\gaia.
This means that there will be a comparable exoplanet occurrence rate
measurement from the \gaia\ data.
It also means that many of the discoveries of the \KT\ and \tess\ missions
will be followed up and precisely measured by the \gaia\ Mission.

\section{Discussion}\sectlabel{discussion}

We have developed a fully automated method to search for the transits of
long-period exoplanets with only one or two observable transits in the
\kepler\ archival light curves.
This method uses probabilistic model comparison to veto non-transit signals.
Applying this method to the brightest \numtargets\ G/K-dwarfs in the \kepler\
target list, we discover \numcands\ systems with likely astrophysical
transits and eclipses.
We fit the light curve for each candidate with a physical generative model and
informative priors on eccentricity and stellar density to estimate the
planet's orbital period.
Simulations of the false positive population~--~the secondary eclipses of
binary systems and background eclipsing binaries~--~suggest that 13 of these
candidates have high probability of being planetary in nature.

We measure the empirical detection efficiency function of our search procedure
by injecting simulated transit signals into the target light curves and
measuring the recovery rate.
By combining the measured detection efficiency and the catalog of exoplanet
candidates, we estimate the integrated occurrence rate of exoplanets with
orbital periods in the range $2-25\unit{years}$ and radii in the range
$0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K-dwarf.
This result is qualitatively consistent with estimates from radial velocity,
microlensing, and direct imaging surveys.

@@

\acknowledgments
It is a pleasure to thank
So Hattori,
Jeff Coughlin,
Angie Wolfgang,
and
Hans-Walter Rix
for helpful contributions to the ideas and code presented here.

>>>>

\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\uw},
    Timothy~D.~Morton\altaffilmark{\princeton},
    David~W.~Hogg\altaffilmark{\scda,\nyu,\mpia,\cds},
    Eric~Agol\altaffilmark{\uw}, and
    Bernhard~Sch\"olkopf\altaffilmark{\mpis}
}

@@

The \kepler\ Mission has discovered thousands of exoplanets and revolutionized
our understanding of their population.
This large, homogeneous catalog of discoveries has enabled rigorous studies of
the occurrence rate of exoplanets and planetary systems as a function of their
physical properties.
Transit surveys like \kepler\ are most sensitive to planets with shorter
orbital periods than Jupiter and Saturn which dominate the dynamics of our
Solar System.
We performed a fully automated search for long-period exoplanets with only one
or two transits in the archival \kepler\ light curves.
When applied to the $\sim 40,000$ brightest Sun-like target stars, this search
produces \numcands\ long-period exoplanet candidates.
Of these candidates, 6 are novel discoveries and 5 are in systems with inner
short-period transiting planets.
Since our method involves no human intervention, we empirically characterize
the completeness and reliability of our search.
Based on these results, we measure the average occurrence rate of exoplanets
smaller than Jupiter with orbital periods longer than two years.

@@

Data from the \kepler\ Mission \citep{Borucki:2011} have been used to discover
thousands of transiting exoplanets.
The systematic nature of these discoveries and careful quantification of
survey selection effects, search completeness, and catalog reliability has
enabled many diverse studies of the detailed frequency and distribution of
exoplanets \citep[for example,][]{Howard:2012, Petigura:2013,
Foreman-Mackey:2014, Dressing:2015, Burke:2015, Mulders:2015}.
So far, these results have been limited to relatively short orbital periods
because existing transit search methods require the observation of at least
three transits within the baseline of the data.
For \kepler, with a baseline of about four years, this sets an absolute upper
limit on the detectable periods of about two years.
In the Solar System, Jupiter~--~with a period of 12 years~--~dominates the
planetary dynamics and, since it would only exhibit at most one transit in the
\kepler\ data, an exo-Jupiter would be missed by most existing transit search
procedures.

@@

The occurrence rates given here should be interpreted with a few caveats in
mind.
First, when we inferred the periods of the planets with only one transit, we
assumed that the period was long enough that no other transit occurred during
the \kepler\ lifetime.
This neglects the small but non-negligible posterior probability~--~less than
one percent for the typical candidate~--~that a second transit might have
occurred in a data gap.
All of the candidates in our catalog are consistent with having periods this
long but the geometric transit probability decreases quickly with orbital
period.
For the purposes of this \paper, we neglect this effect because its rigorous
treatment is subtle but comment that this would only ever decrease the
occurrence rate estimate.

% This occurrence rate estimate~--~and all other results based on transit
% surveys~--~is affected by Malmquist bias.
% For a transit survey, this bias enters in two ways: \emph{(a)} contamination
% of the sample by giants, and \emph{(b)} discrepancy

@@

\citet{Clanton:2014} studied the occurrence rate of long-period giant planets
orbiting M dwarfs by combining results from radial velocity and microlensing
surveys.
In the period and mass range $10^3-10^4\unit{days}$ and $10-10^4\,M_\oplus$,
they find a mean occurrence rate density of
\begin{eqnarray}
\frac{\dd^2 N}{\dd\ln M\,\dd\ln P}
    &\lesssim& 0.026
\end{eqnarray}
per M dwarf.
This result is slightly lower than our estimated rate for a similar range of
masses and periods but around G/K dwarfs.
This difference is consistent with previous results that cooler stars host
fewer long-period giant planets \citep[for example][]{Cumming:2008}.

@@

\tablenotetext{a}{The rate density is measured in natural logarithmic units;
see \eq{massocc}.}
\tablecomments{These values are computed assuming that the occurrence rate is
flat in the logarithmic parameters.}
\end{deluxetable}
\end{floattable}

@@

The single-visit precision of \gaia\ will vary with magnitude but is expected
to be on the order of 40\,$\mu$as at these magnitudes.
In detail the confidence with which an exoplanet can be detected or measured
in the final \gaia\ data depends on this precision, the number of crossings of
the star through the \gaia\ focal plane, and details of how the projected
orbit is sampled by the time history of the focal-plane crossings.
However, it is not expected that \gaia\ can detect or precisely measure
exoplanet-induced astrometric wobbles that are much smaller in amplitude than
the single-visit precision \citep{Perryman:2014}.

The primary stars in the \kepler\  Field are typically at distances of $\sim
500$\,pc, and typical mass ratios are in the $10^{-4}$ range.
We therefore expect astrometric amplitudes in the 0.3 to 3\,$\mu$as range.
These planets will not be detectable or measurable in the \gaia\ data under
any circumstances.
However, similar planets around closer stars \emph{will} be detectable with
\gaia.
This means that there will be a comparable exoplanet occurrence rate
measurement from the \gaia\ data.
It also means that many of the discoveries of the \KT\ and \tess\ missions
could be followed up and precisely measured by the \gaia\ Mission.

\section{Summary}\sectlabel{summary}

We have developed a fully automated method to search for the transits of
long-period exoplanets with only one or two observable transits in the
\kepler\ archival light curves.
This method uses probabilistic model comparison to veto non-transit signals.
Applying this method to the brightest \numtargets\ G/K dwarfs in the \kepler\
target list, we discover \numcands\ systems with likely astrophysical
transits and eclipses.
We fit the light curve for each candidate with a physical generative model and
informative priors on eccentricity and stellar density to estimate the
planet's orbital period.
Simulations of the false positive population~--~the secondary eclipses of
binary systems and background eclipsing binaries~--~suggest that 13 of these
candidates have high probability of being planetary in nature.

We measure the empirical detection efficiency function of our search procedure
by injecting simulated transit signals into the target light curves and
measuring the recovery rate.
By combining the measured detection efficiency and the catalog of exoplanet
candidates, we estimate the integrated occurrence rate of exoplanets with
orbital periods in the range $2-25\unit{years}$ and radii in the range
$0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K dwarf.
This result is qualitatively consistent with estimates from radial velocity,
microlensing, and direct imaging surveys.

\dfmtodo{More words here about comparison.}

@@

\acknowledgments
It is a pleasure to thank
Jeff Coughlin,
So Hattori,
Hans-Walter Rix,
Dun Wang,
and
Angie Wolfgang
for helpful contributions to the ideas and code presented here.
